Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-15 MDPI/response_letter.tex

% modify the page to use the space more efficiently
\addtolength{\textwidth}{1.5cm}
\addtolength{\textheight}{2.0cm}

\textbf{Reviewer 1}
\textit{}

\begin{enumerate}
\item \textit{The main findings of your results should be highlighted in abstract} 
We have rewritten the abstract. The abstract now contains main findings of our paper.

\item \textit{Please do not separate introduction in three sections combine with problem and technology you used and challenges and your solutions.}
Corrected. We have rewritten and improved the Introduction.

@@

\end{enumerate}

\textbf{Reviewer 3}

\textit{}
\begin{enumerate}
\item \textit{The full stop in the title should be revised.}
Noted. Revised.
\item \textit{The abstract needs to be revised and be more attractive. The research gap, novelty and main findings should be concisely mentioned in the abstract.}
We have rewritten the abstract. We believe that the abstract is much more attractive now.
\item \textit{In this current shape, the manuscript looks like a report. The authors have to revise the flow of the context to attract the readers.}
We have revised and changed the manuscript to be more attractive for the readers. 
\item \textit{The manuscript must be improved by checking once again in English and technical writing. }
We improved the writing style of the manuscript and corrected the grammatical errors.

\item \textit{The whole manuscript must be supported by enough recent references. Revise the whole context.}
We added more recent references.
\item \textit{The beginning of the introduction part must be revised to be more attractive.}
Corrected. We haǘe rewritten and improved the Introduction section.
\item \textit{The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part  \href{https://doi.org/10.1016/j.jwpe.2022.102847}{https://doi.org/10.1016/j.jwpe.2022.102847} ; \href{https://doi.org/10.1016/j.ceramint.2022.05.151}{https://doi.org/10.1016/j.ceramint.2022.05.151} ; 
\href{https://doi.org/10.3390/catal12050500}{https://doi.org/10.3390/catal12050500} ; 
\href{https://doi.org/10.1007/s11356-022-21160-7}{https://doi.org/10.1007/s11356-022-21160-7} ; 
\href{https://doi.org/10.3390/ma15134547}{https://doi.org/10.3390/ma15134547}. 
Then, highlight the water desalination technologies and Gibbs ensemble (\href{https://doi.org/10.3390/nano10020293}{https://doi.org/10.3390/nano10020293}).}
Corrected. We added the citations, which are relevant to the studied problems, in their appropriate places.
\item \textit{Authors should indicate a clear gap in knowledge which this study seeks to bridge, and potentially contribute to knowledge. }
The purpose of our paper is to show that desalination using polyelectrolyte hydrogels is a cheap and therefore competitive alternative to reverse osmosis.
We highlighted this idea in the Introduction and Conclusion sections.
\item \textit{L 125-126, meaningless sentence. Revise the whole context.}
Corrected.
\item \textit{All sections/subsections titles must be revised to be expressive.}
Corrected. We have rewritten and improved not only the Introduction, but the sections Model and Methods, Results, Conclusions as well.
\item \textit{Statistical physics considerations including setup and calculations should be added.}
We added the paragraph about Gibbs ensemble.
\item \textit{The authors should identify the limitations of this study and the recommended future studies in the conclusion part.
}
We identified the study limitations and considered the implications and future perspectives of the study. We added the respective paragraphs.
\end{enumerate}

### 2022-09-15 gibbs.tex
Update gibbs.tex

\section{Introduction\label{sec: intro}}
\subsection{Water desalination technologies}

\todo[inline]{
The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part
https://doi.org/10.1016/j.jwpe.2022.102847 \cite{baaloudj2022_1}\\
https://doi.org/10.1016/j.ceramint.2022.05.151 \cite{shahzad2022}\\
https://doi.org/10.3390/catal12050500 \cite{baaloudj2022}\\
https://doi.org/10.1007/s11356-022-21160-7 \cite{guesmi2022}\\
https://doi.org/10.3390/ma15134547 \cite{kane2022}\\. 
Then, highlight the water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
}

Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.

@@

>>>>

\section{Introduction\label{sec: intro}}

Waste water treatment and technology is one of the greatest concerns of modern sustainable society. 
The water has to be disposed of both biological \cite{guesmi2022} and chemical \cite{baaloudj2022_1,shahzad2022} pollutants.
Most imporatntly, water treatment technologies have to be prepared for the still increasing need for production of potable water from the brine, \ie for desalination.

\subsection{Water desalination technologies}
Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.

@@

TODO Then, highlight the water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
